A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-09-24 paper/paper.tex
paper: label diagrams; kerning problem with 0\star0
paper: fix kerning for \star
paper: fix simplicial dia

@@

We exploit the connection between iterated unary parametricity and augmented simplicial sets and between binary parametricity and cubical sets to present a uniform construction of both semi-simplicial semi-cubical sets obtained by applying simple rules iterating parametricity.  In contrast to the presheaf presentation of semi-simplicial and semi-cubical sets, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}. That is, instead of having the set of semi-simplices or semi-cubes in dimension $n+1$
\emph{fibered} over the set of semi-simplices or semi-cubes in dimension $n$, we consider families of semi-simplices and semi-cubes indexed over their faces.

@@

\begin{example}[$\DeltaPlus^2$]
  \begin{equation*}
    \begin{tikzcd}
      \star0 \arrow[r, dash, "\star\star"] & 0\star
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{example}[$\DeltaPlus^3$]
  \begin{equation*}
    \begin{tikzcd}
      & 00\star \arrow[dr, dash, "0\star\star"] & \\
      \star00 \arrow[rr, dash, "\star\star0"]\arrow[ur, dash, "\star0\star"] && 0\star0
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

\begin{example}[$\Cube^1$]
  \begin{equation*}
    \begin{tikzcd}
      0 \arrow[r, "\star", dash] & 1
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{example}[$\Cube^2$]
  \begin{equation*}
    \begin{tikzcd}
      (0, 1) \arrow[r, dash] & (1, 1) \arrow[d, dash] \\
      (0, 0) \arrow[u, dash] & (1, 0) \arrow[l, dash]
    \end{tikzcd}
  \end{equation*}
\end{example}

>>>>

% Kerning for star
\newcommand{\kstar}{{\star}}

@@

We exploit the connection between iterated unary parametricity and augmented simplicial sets, and between iterated binary parametricity and cubical sets to present a uniform construction of both semi-simplicial semi-cubical sets obtained by applying simple rules iterating parametricity.  In contrast to the presheaf presentation of semi-simplicial and semi-cubical sets, our uniform construction, which we call \emph{$\nu$-sets}, is \emph{indexed}. That is, instead of having the set of semi-simplices or semi-cubes in dimension $n+1$
\emph{fibered} over the set of semi-simplices or semi-cubes in dimension $n$, we consider families of semi-simplices and semi-cubes indexed over their faces.

@@

\begin{example}[$\DeltaPlus^2$]
  \begin{equation*}
    \begin{tikzcd}
      \kstar0 \arrow[r, dash, "\kstar\kstar"] & 0\kstar
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{example}[$\DeltaPlus^3$]
  \begin{equation*}
    \begin{tikzcd}
      & |[alias=F]|00\kstar \arrow[ddr, dash, "0\kstar\kstar"] & \\\\
      \kstar00 \arrow[rr, dash, "\kstar\kstar0"{name=T, below}]\arrow[uur, dash, "\kstar0\kstar"] && 0\kstar0 \\
      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar\kstar" description]
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

\begin{example}[$\Cube^1$]
  \begin{equation*}
    \begin{tikzcd}
      0 \arrow[r, "\kstar", dash] & 1
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{example}[$\Cube^2$]
  \begin{equation*}
    \begin{tikzcd}
      (0, 1) \arrow[r, dash, "\kstar1"{name=F}] \arrow[d, dash, "0\kstar" left] & (1, 1) \arrow[d, dash, "1\kstar"] \\
      (0, 0) \arrow[r, dash, "\kstar0"{name=T, below}] & (1, 0) \\
      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar" description]
    \end{tikzcd}
  \end{equation*}
\end{example}
